---
title: "Epitope and nucleotide diversity"
author: "Christine Markwalter"
date: "12/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dpi=300)
grDevices::pdf.options(useDingbats = FALSE)
library(Biostrings)
#library(ggplot2) #redundant
#library(dplyr) #redundant
library(tidyverse)
library(ggpmisc)
library(lubridate)
library(randomForest)

library(survival)
library(survminer)
library(coxme)
library(forestplot)

library(ggfortify)
library(ggseqlogo)
library(arsenal)

library(ggpubr)
```

#Human data
```{r}
HumanData<-read.csv("data/original/spat21_human_final_censored_data_for_dissertation_with_exposure_outcome_1MAR2020.csv")

HDS<-HumanData %>% 
  dplyr::select(sample_name_dbs,unq_memID,sample_id_date,main_outcome_primary_case_def,main_exposure_primary_case_def)%>%
  filter(main_exposure_primary_case_def == "asymptomatic infection" | main_outcome_primary_case_def == "symptomatic infection") %>%
  mutate(symptomatic_status = ifelse(is.na(main_exposure_primary_case_def), as.character(main_outcome_primary_case_def),as.character(main_exposure_primary_case_def))) %>%
  dplyr::select(-c(main_exposure_primary_case_def,main_outcome_primary_case_def))
```


# csp

## Load sequence data
```{r, warning=F,message=F}

csp_seqs <- Biostrings::readDNAStringSet("data/original/spat21_CSP_uniqueSeqs_final_censored.fasta")


csp_haplotypes<-read.csv("data/original/spat21_csp_summarized_haplotype_list_31DEC2019.csv")

head(csp_seqs)
head(csp_haplotypes)
```


## Remove mozzies

```{r, warning=F,message=F}
csp_haplotypes = csp_haplotypes %>%
  filter(!(str_detect(sample_name_dbs,"H")) & !(str_detect(sample_name_dbs,"A")) | sample_name_dbs == "K14-170717-1A-R") 

#make list of haplotypes found in human samples
csp_haplotypelist=csp_haplotypes%>%
  separate_rows(haplotype_list)%>%
  summarise(HType=paste(unique(haplotype_list)))

#Replace haplotype names to match them with seq names
csp_haplotypelist$HType=sub('.', '', csp_haplotypelist$HType)
csp_haplotypelist=csp_haplotypelist%>%
  mutate(seqs=paste("Seq",HType,sep=""))

length(csp_haplotypelist$HType)

```

## Translate nucleotide sequence to AAs

```{r, warning=FALSE}
#CSP is translated in reverse and starting at the 3rd nucleotide
csp_DNAseqrev<-reverseComplement(csp_seqs)
csp_DNAseqrev <- DNAStringSet(csp_DNAseqrev, start=3)
length(unique(csp_DNAseqrev))

csp_AAseq<-translate(csp_DNAseqrev, genetic.code=GENETIC_CODE, no.init.codon=FALSE,
             if.fuzzy.codon="error")

csp_AAseqmatrix<-consensusMatrix(csp_AAseq, as.prob = TRUE)
csp_AArevmatrixvariant=csp_AAseqmatrix
```

Change sequences to dataframe and combine them with haplotype name to match with human data
```{r}

csp_AAdf<-as.data.frame(csp_AAseq)
csp_AAdf<-cbind(seq = rownames(csp_AAdf), csp_AAdf)
rownames(csp_AAdf)<-1:nrow(csp_AAdf)
csp_AAdf$HType=paste("H",sub('...', '', csp_AAdf$seq),sep="")
length(unique(csp_AAdf$x))

```


filter protein sequences only in haplotypes present in human samples
```{r}
csp_AAdf <- csp_AAdf%>%
  filter(seq %in% csp_haplotypelist$seqs)
length(unique(csp_AAdf$x))
```


removing sequences with stop codons
```{r,eval=T}
csp_AAdf$nstopcodon <- vcountPattern("*", csp_AAdf$x, max.mismatch=0)
csp_AAdf%>%
  group_by(nstopcodon)%>%
  count()
cat("number of stopcodons:", sum(csp_AAdf$nstopcodon), "\n")
csp_AAdf=csp_AAdf%>%
  filter(nstopcodon==0)
cat("number of sequences without stop codons", length(csp_AAdf$x), "\n")
cat("number of unique sequences",length(unique(csp_AAdf$x)))

```

Separating each samples haplotypes into individual rows and make them into a list of unique haplotypes

```{r, warning=F,message=F}
csp_haplotypesExp<-tidyr::separate_rows(csp_haplotypes, haplotype_list, sep=",")
csp_haplotypesExp$HType<-csp_haplotypesExp$haplotype_list
csp_MergHaploAA<-merge(csp_haplotypesExp,csp_AAdf,by="HType") %>%
  select(-haplotype_list)
dim(csp_MergHaploAA)
#We lose 7 haplotype occurences because upon merging due to removing sequences with stop codons.

csp_MergedData<-merge(HDS,csp_MergHaploAA,by="sample_name_dbs") %>%
  select(-haplotype_reads, -nstopcodon) %>%
  rowwise() %>%
  mutate(cd4_epitope = paste0(substr(x,25,25),substr(x,28,28), substr(x,29,29), substr(x,31,31)), cd8_epitope = paste0(substr(x,59,59),substr(x,64,64), substr(x,66,66), substr(x,68,68)), combined_epitope = paste0(cd4_epitope, cd8_epitope), dv10_epitope = paste0(substr(x,5,5), substr(x,6,6), substr(x,8,8), substr(x, 10,10)))
```


# cd4
```{r}

cd4_sunburst <- csp_MergedData %>%
  group_by(cd4_epitope, HType) %>%
  summarise(n_samples = n_distinct(sample_name_dbs))


cd4_sunburst <- cd4_sunburst %>%
  mutate(cd4_epitope = as.factor(cd4_epitope) %>% fct_reorder(n_samples, sum)) %>%
  arrange(cd4_epitope, n_samples) %>%
  mutate(HType = as.factor(HType) %>% fct_reorder2(cd4_epitope, n_samples))
  

lvl0 <- tibble(name = "Parent", value = 0, level = 0, fill = NA)
lvl1 <- cd4_sunburst %>%
  group_by(cd4_epitope) %>%
  summarise(value = sum(n_samples)) %>%
  ungroup() %>%
  rename(name = cd4_epitope) %>%
  mutate(level = 1, fill = name)

lvl2 <- cd4_sunburst %>%
  select(name = HType, value = n_samples, fill = cd4_epitope) %>%
  mutate(level = 2)


combined <- bind_rows(lvl0, lvl1, lvl2) %>%
  arrange(level, value)


cd4_sunburst_plot <- ggplot(combined, aes(x = as.factor(level), y = value, fill = fct_reorder(fill, value, sum), alpha = as.factor(level))) +
  geom_col(width = 1, color = "white", size = 0.25, position = "stack") +
  geom_text(data = combined %>% filter(level == 1, value > 10), mapping = aes(label = name), angle = c(-90,-90,-90,-75,-75,-60,-60,-45,-45,-45,-30,-20,-10,0,20,30,45,0,0,0,0,0,0), size = 2.5, position = position_stack(vjust = 0.5)) +
  annotate("text",x = 1.1, y = 1, label = "Epitope type")+
  annotate("text",x = 3.7, y = 1, label = "Haplotype") +
  coord_polar(theta = "y") +
  scale_alpha_manual(values = c("0" = 0, "1" = 1, "2" = 0.7), guide = "none") +
  scale_x_discrete(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  scale_fill_manual(values = c("#696969", "#556b2f","#8b4513","#483d8b","#008000","#008080","#000080","#9acd32","#32cd32","#8fbc8f","#8b008b","#b03060","#d2b48c","#00ced1","#ffa500","#dc143c","#00bfff","#f4a460","#0000ff","#f0e68c","#fa8072","#6495ed","#dda0dd","#b0e0e6","#ff1493","#7b68ee","#ee82ee"))+
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")

cd4_sunburst_plot

saveRDS(cd4_sunburst_plot, "figures/robj/cd4_sunburst.RDS")

ggsave(plot = cd4_sunburst_plot, "figures/cd4_sunburst.png", width = 6, height = 6)


```



# cd8
```{r}

cd8_sunburst <- csp_MergedData %>%
  group_by(cd8_epitope, HType) %>%
  summarise(n_samples = n_distinct(sample_name_dbs))


cd8_sunburst <- cd8_sunburst %>%
  mutate(cd8_epitope = as.factor(cd8_epitope) %>% fct_reorder(n_samples, sum)) %>%
  arrange(cd8_epitope, n_samples) %>%
  mutate(HType = as.factor(HType) %>% fct_reorder2(cd8_epitope, n_samples))
  

lvl0 <- tibble(name = "Parent", value = 0, level = 0, fill = NA)
lvl1 <- cd8_sunburst %>%
  group_by(cd8_epitope) %>%
  summarise(value = sum(n_samples)) %>%
  ungroup() %>%
  rename(name = cd8_epitope) %>%
  mutate(level = 1, fill = name)

lvl2 <- cd8_sunburst %>%
  select(name = HType, value = n_samples, fill = cd8_epitope) %>%
  mutate(level = 2)


combined <- bind_rows(lvl0, lvl1, lvl2) %>%
  arrange(level, value)

cd8_sunburst_plot <- ggplot(combined, aes(x = as.factor(level), y = value, fill = fct_reorder(fill, value, sum), alpha = as.factor(level))) +
  geom_col(width = 1, color = "white", size = 0.25, position = "stack") +
  geom_text(data = combined %>% filter(level == 1, value > 10), mapping = aes(label = name), size = 2.5, position = position_stack(vjust = 0.5), angle = c(-90,-90,-75,-70,-45,0,0,0,0,0,0)) +
  annotate("text",x = 1.1, y = 1, label = "Epitope type")+
  annotate("text",x = 3.7, y = 1, label = "Haplotype") +
  coord_polar(theta = "y") +
  scale_alpha_manual(values = c("0" = 0, "1" = 1, "2" = 0.7), guide = "none") +
  scale_x_discrete(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  scale_fill_manual(values = c("#008080","#000080","#9acd32","#32cd32","#8fbc8f","#8b008b","#b03060","#d2b48c","#00ced1","#ffa500","#dc143c","#00bfff","#f4a460","turquoise")) +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")

cd8_sunburst_plot

saveRDS(cd8_sunburst_plot, "figures/robj/cd8_sunburst.RDS")

ggsave(plot = cd8_sunburst_plot, "figures/cd8_sunburst.png", width = 6, height = 6)



```


# dv10
```{r}

dv10_sunburst <- csp_MergedData %>%
  group_by(dv10_epitope, HType) %>%
  summarise(n_samples = n_distinct(sample_name_dbs))


dv10_sunburst <- dv10_sunburst %>%
  mutate(dv10_epitope = as.factor(dv10_epitope) %>% fct_reorder(n_samples, sum)) %>%
  arrange(dv10_epitope, n_samples) %>%
  mutate(HType = as.factor(HType) %>% fct_reorder2(dv10_epitope, n_samples))
  

lvl0 <- tibble(name = "Parent", value = 0, level = 0, fill = NA)
lvl1 <- dv10_sunburst %>%
  group_by(dv10_epitope) %>%
  summarise(value = sum(n_samples)) %>%
  ungroup() %>%
  rename(name = dv10_epitope) %>%
  mutate(level = 1, fill = name)

lvl2 <- dv10_sunburst %>%
  select(name = HType, value = n_samples, fill = dv10_epitope) %>%
  mutate(level = 2)


combined <- bind_rows(lvl0, lvl1, lvl2) %>%
  arrange(level, value)

dv10_sunburst_plot <- ggplot(combined, aes(x = as.factor(level), y = value, fill = fct_reorder(fill, value, sum), alpha = as.factor(level))) +
  geom_col(width = 1, color = "white", size = 0.25, position = "stack") +
  geom_text(data = combined %>% filter(level == 1, value > 10), mapping = aes(label = name), size = 2.5, position = position_stack(vjust = 0.5), angle = c(-90,-90,0,0,0)) +
  annotate("text",x = 1.1, y = 1, label = "Epitope type")+
  annotate("text",x = 3.7, y = 1, label = "Haplotype") +
  coord_polar(theta = "y") +
  scale_alpha_manual(values = c("0" = 0, "1" = 1, "2" = 0.7), guide = "none") +
  scale_x_discrete(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  scale_fill_manual(values = c("#000080","#32cd32","#8fbc8f","#8b008b","#b03060","#d2b48c","#00ced1","#ffa500","#dc143c")) +
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")

dv10_sunburst_plot

saveRDS(dv10_sunburst_plot, "figures/robj/dv10_sunburst.RDS")

ggsave(plot = dv10_sunburst_plot, "figures/dv10_sunburst.png", width = 6, height = 6)



```



#ama
## Load sequence data
```{r, warning=F,message=F}

ama_seqs <- Biostrings::readDNAStringSet("data/original/spat21_AMA_uniqueSeqs_final_censored.fasta")


ama_haplotypes<-read.csv("data/original/spat21_ama_summarized_haplotype_list_31DEC2019.csv")

head(ama_seqs)
head(ama_haplotypes)
```


## Remove mozzies

```{r, warning=F,message=F}
ama_haplotypes = ama_haplotypes %>%
  filter(!(str_detect(sample_name_dbs,"H")) & !(str_detect(sample_name_dbs,"A")) | sample_name_dbs == "K14-170717-1A-R") 

#make list of haplotypes found in human samples
ama_haplotypelist=ama_haplotypes%>%
  separate_rows(haplotype_list)%>%
  summarise(HType=paste(unique(haplotype_list)))

#Replace haplotype names to match them with seq names
ama_haplotypelist$HType=sub('.', '', ama_haplotypelist$HType)
ama_haplotypelist=ama_haplotypelist%>%
  mutate(seqs=paste("Seq",HType,sep=""))

length(ama_haplotypelist$HType)

```

## Translate nucleotide sequence to AAs

```{r, warning=FALSE}

length(unique(ama_seqs))
#Correct start of translation AMA is translated from the 3rd nucleotide
ama_seqs3<- DNAStringSet(ama_seqs, start=3)
ama_AAseq=translate(ama_seqs3)
length(unique(ama_AAseq))

ama_AAseqmatrix<-consensusMatrix(ama_AAseq, as.prob = TRUE)

```

Change sequences to dataframe and combine them with haplotype name to match with human data
```{r}

ama_AAdf<-as.data.frame(ama_AAseq)
ama_AAdf<-cbind(seq = rownames(ama_AAdf), ama_AAdf)
rownames(ama_AAdf)<-1:nrow(ama_AAdf)
ama_AAdf$HType=paste("H",sub('...', '', ama_AAdf$seq),sep="")
length(unique(ama_AAdf$x))

```

filter protein sequences only in haplotypes present in human samples
```{r}
ama_AAdf <- ama_AAdf%>%
  filter(seq %in% ama_haplotypelist$seqs)
length(unique(ama_AAdf$x))
```


removing sequences with stop codons
```{r,eval=T}
ama_AAdf$nstopcodon <- vcountPattern("*", ama_AAdf$x, max.mismatch=0)
ama_AAdf%>%
  group_by(nstopcodon)%>%
  count()
cat("number of stopcodons:", sum(ama_AAdf$nstopcodon), "\n")
ama_AAdf=ama_AAdf%>%
  filter(nstopcodon==0)
cat("number of sequences without stop codons", length(ama_AAdf$x), "\n")
cat("number of unique sequences",length(unique(ama_AAdf$x)))

```

Separating each samples haplotypes into individual rows and make them into a list of unique haplotypes

```{r, warning=F,message=F}
ama_haplotypesExp<-tidyr::separate_rows(ama_haplotypes, haplotype_list, sep=",")
ama_haplotypesExp$HType<-ama_haplotypesExp$haplotype_list
ama_MergHaploAA<-merge(ama_haplotypesExp,ama_AAdf,by="HType") %>%
  select(-haplotype_list)
dim(ama_MergHaploAA)
#We lose 7 haplotype occurences because upon merging due to removing sequences with stop codons.

ama_MergedData<-merge(HDS,ama_MergHaploAA,by="sample_name_dbs") %>%
  select(-haplotype_reads, -nstopcodon) %>%
  rowwise() %>%
  mutate(ama_epitope = paste0(substr(x,36,36),substr(x,44,44), substr(x,77,77), substr(x,90,90)))

c1L_MergedData<-merge(HDS,ama_MergHaploAA,by="sample_name_dbs") %>%
  select(-haplotype_reads, -nstopcodon) %>%
  rowwise() %>%
  mutate(ama_epitope = paste0(substr(x,44,44),substr(x,47,47), substr(x,48,48), substr(x,53,53)))

```

## plot
ama top 4
```{r}

ama_sunburst <- ama_MergedData %>%
  group_by(ama_epitope, HType) %>%
  summarise(n_samples = n_distinct(sample_name_dbs))


ama_sunburst <- ama_sunburst %>%
  mutate(ama_epitope = as.factor(ama_epitope) %>% fct_reorder(n_samples, sum)) %>%
  arrange(ama_epitope, n_samples) %>%
  mutate(HType = as.factor(HType) %>% fct_reorder2(ama_epitope, n_samples))
  

lvl0 <- tibble(name = "Parent", value = 0, level = 0, fill = NA)
lvl1 <- ama_sunburst %>%
  group_by(ama_epitope) %>%
  summarise(value = sum(n_samples)) %>%
  ungroup() %>%
  rename(name = ama_epitope) %>%
  mutate(level = 1, fill = name)

lvl2 <- ama_sunburst %>%
  select(name = HType, value = n_samples, fill = ama_epitope) %>%
  mutate(level = 2)


combined <- bind_rows(lvl0, lvl1, lvl2) %>%
  arrange(level, value)


ama_sunburst_plot <- ggplot(combined, aes(x = as.factor(level), y = value, fill = fct_reorder(fill, value, sum), alpha = as.factor(level))) +
  geom_col(width = 1, color = "white", size = 0.25, position = "stack") +
  geom_text(data = combined %>% filter(level == 1, value > 21 ), mapping = aes(label = name), angle = c(-75,-75,-65,-60,-45,-30,-30,-15,-15,0,10,20,45,45,60,60,0,0,0,0,0,0,0), size = 2.5, position = position_stack(vjust = 0.5)) +
  annotate("text",x = 1.1, y = 1, label = "Epitope type")+
  annotate("text",x = 3.7, y = 1, label = "Haplotype") +
  coord_polar(theta = "y") +
  scale_alpha_manual(values = c("0" = 0, "1" = 1, "2" = 0.7), guide = "none") +
  scale_x_discrete(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  scale_fill_manual(values = c("#808080",	"#2f4f4f",	"#556b2f",	"#8b4513",	"#a52a2a", "#2e8b57",	"#228b22",	"#191970",	"#808000",	"#008b8b",	"#cd853f",	"#4682b4",	"#9acd32",	"#00008b",	"#32cd32",	"#daa520",	"#8fbc8f",	"#800080",	"#b03060",	"#d2b48c",	"#ff0000",	"#00ced1",	"#ff8c00",	"#ffd700",	"#0000cd",	"#00ff00",	"#ba55d3",	"#00fa9a",	"#00bfff",	"#a020f0",	"#f08080",	"#adff2f",	"#ff6347",	"#d8bfd8",	"#ff00ff",	"#1e90ff",	"#f0e68c",	"#b0e0e6",	"#90ee90",	"#7b68ee",	"#7fffd4",	"#ff69b4"))+
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")

ama_sunburst_plot

saveRDS(ama_sunburst_plot, "figures/robj/ama_sunburst.RDS")

ggsave(plot = ama_sunburst_plot, "figures/ama_sunburst.png", width = 6, height = 6)


```


c1L top 4
```{r}
c1L_sunburst <- c1L_MergedData %>%
  group_by(ama_epitope, HType) %>%
  summarise(n_samples = n_distinct(sample_name_dbs))


c1L_sunburst <- c1L_sunburst %>%
  mutate(ama_epitope = as.factor(ama_epitope) %>% fct_reorder(n_samples, sum)) %>%
  arrange(ama_epitope, n_samples) %>%
  mutate(HType = as.factor(HType) %>% fct_reorder2(ama_epitope, n_samples))
  

lvl0 <- tibble(name = "Parent", value = 0, level = 0, fill = NA)
lvl1 <- c1L_sunburst %>%
  group_by(ama_epitope) %>%
  summarise(value = sum(n_samples)) %>%
  ungroup() %>%
  rename(name = ama_epitope) %>%
  mutate(level = 1, fill = name)

lvl2 <- c1L_sunburst %>%
  select(name = HType, value = n_samples, fill = ama_epitope) %>%
  mutate(level = 2)


combined <- bind_rows(lvl0, lvl1, lvl2) %>%
  arrange(level, value)


c1L_sunburst_plot <- ggplot(combined, aes(x = as.factor(level), y = value, fill = fct_reorder(fill, value, sum), alpha = as.factor(level))) +
  geom_col(width = 1, color = "white", size = 0.25, position = "stack") +
  geom_text(data = combined %>% filter(level == 1, value > 21 ), mapping = aes(label = name), angle = c(-90,-90,-80,-75,-65,-60, -45,-30,0,0,30,45,0,0,0,0), size = 2.5, position = position_stack(vjust = 0.5)) +
  annotate("text",x = 1.1, y = 1, label = "Epitope type")+
  annotate("text",x = 3.7, y = 1, label = "Haplotype") +
  coord_polar(theta = "y") +
  scale_alpha_manual(values = c("0" = 0, "1" = 1, "2" = 0.7), guide = "none") +
  scale_x_discrete(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  scale_fill_manual(values = c("#00ff00", "#2f4f4f", "#00fa9a","#b0e0e6", "#8b4513",	 "#2e8b57",	"#191970",	"#008b8b",		"#4682b4",	"#00008b",	"#daa520",	"#800080",	"#d2b48c",	"#00ced1",	"#ff8c00",	"#ffd700",	"#a020f0",	"#adff2f",	"#d8bfd8",	"#1e90ff"))+
  labs(x = NULL, y = NULL) +
  theme_minimal() +
  theme(legend.position = "none")

c1L_sunburst_plot

saveRDS(c1L_sunburst_plot, "figures/robj/c1L_sunburst.RDS")

ggsave(plot = c1L_sunburst_plot, "figures/c1L_sunburst.png", width = 6, height = 6)


```


#MOI figure
```{r}

csp_moi <- csp_MergedData %>%
  group_by(sample_name_dbs) %>%
  summarise(HType_moi = mean(haplotype_number), cd4_moi = n_distinct(cd4_epitope), cd8_moi = n_distinct(cd8_epitope), combined_moi = n_distinct(combined_epitope), dv10_moi = n_distinct(dv10_epitope))

ama_moi <- ama_MergedData %>%
  group_by(sample_name_dbs) %>%
  summarise(HType_moi = mean(haplotype_number), ama_moi = n_distinct(ama_epitope))

c1L_moi <- c1L_MergedData %>%
  group_by(sample_name_dbs) %>%
  summarise(HType_moi = mean(haplotype_number), c1L_moi = n_distinct(ama_epitope))

my.formula <- y ~ x+0


cd4_moi_plot <- ggplot(csp_moi,aes(x=HType_moi, y=cd4_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("CD4+ epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

cd8_moi_plot <- ggplot(csp_moi,aes(x=HType_moi, y=cd8_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("CD8+ epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

combined_moi_plot <- ggplot(csp_moi,aes(x=HType_moi, y=combined_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("Combined CSP epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

dv10_moi_plot <- ggplot(csp_moi,aes(x=HType_moi, y=dv10_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("DV10 epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

ama_moi_plot <- ggplot(ama_moi,aes(x=HType_moi, y=ama_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("AMA-1 epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

c1L_moi_plot <- ggplot(c1L_moi,aes(x=HType_moi, y=c1L_moi))+
  geom_point(alpha=0.5, position = "jitter")+
  coord_cartesian(xlim=c(0,18),ylim=c(0,18))+
  geom_smooth(method = lm,color="black")+
  labs(title=paste0("c1L epitope MOI corr."))+
  theme_bw()+
  stat_poly_eq(formula = my.formula,
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
               parse = TRUE)+
  xlab("Haplotype MOI")+
  ylab("Epitope MOI")

cd4_moi_plot
cd8_moi_plot
combined_moi_plot
dv10_moi_plot
ama_moi_plot
c1L_moi_plot

saveRDS(cd4_moi_plot, "figures/robj/cd4_moi_plot.RDS")
saveRDS(cd8_moi_plot, "figures/robj/cd8_moi_plot.RDS")
saveRDS(combined_moi_plot, "figures/robj/combined_moi_plot.RDS")
saveRDS(dv10_moi_plot, "figures/robj/dv10_moi_plot.RDS")
saveRDS(ama_moi_plot, "figures/robj/ama_moi_plot.RDS")
saveRDS(c1L_moi_plot, "figures/robj/c1L_moi_plot.RDS")


```


# Combining figures
```{r}
# combined_fig <- ggarrange(ggarrange(cd4_moi_plot +
#                       labs(x = NULL, y = NULL),
#             cd4_sunburst_plot,
#             nrow = 1),
#   ggarrange(cd8_moi_plot +
#               labs(x = NULL),
#             cd8_sunburst_plot,
#             nrow = 1),
#   ggarrange(ama_moi_plot +
#               labs(y = NULL),
#             ama_sunburst_plot,
#             nrow = 1),
#   ncol = 1)
# 
# ggsave(plot = combined_fig, "epitopes/MozzieAminoAcidAnalysis/cfm_figures/moi_sunburst.png", width = 9, height = 12)
# 
# 
# alt_combined_fig <- ggarrange(ggarrange(cd4_sunburst_plot +
#                                           labs(title = "CD4+") +
#                                           theme(plot.title = element_text(hjust = 0.5), plot.margin = unit(c(-2,0,-5,0), "cm")),
#             cd8_sunburst_plot +
#                                           labs(title = "CD8+") +
#                                           theme(plot.title = element_text(hjust = 0.5), plot.margin = unit(c(-2,0,-5,0), "cm")),
#             ama_sunburst_plot +
#                                           labs(title = "AMA-1") +
#                                           theme(plot.title = element_text(hjust = 0.5), plot.margin = unit(c(-2,0,-5,0), "cm")),
#             nrow = 1,
#             widths = c(1,1,1)),
#           ggarrange(NULL,
#             cd4_moi_plot +
#               labs(x = NULL, title = NULL) +
#               theme(plot.margin = unit(c(-4,0,0,0), "cm")),
#             NULL,
#             cd8_moi_plot +
#               labs(y = NULL, title = NULL) +
#               theme(plot.margin = unit(c(-4,0,0,0), "cm")),
#             NULL,
#             ama_moi_plot +
#               labs(x = NULL, y = NULL, title = NULL)+
#               theme(plot.margin = unit(c(-4,0,0,0), "cm")),
#             NULL,
#             nrow = 1,
#             widths = c(0.1,1.1,0.4,1,0.4,1,0.2),
#             align = "h"),
#           nrow = 2,
#           heights = c(6,1),
#           align = "v")
# 
# 
# ggsave(plot = alt_combined_fig, "epitopes/MozzieAminoAcidAnalysis/cfm_figures/alt_moi_sunburst.png", width = 16, height = 12)


```


rmarkdown::render("C:/Users/cf199/Box/O\'Meara-Taylor Postdoc//mozzie_epitope_analysis/code/epitope_diversity.Rmd", output_file= paste0("epitope_diversity_", format(now(), "%Y%m%d_%H%M%S_"), ".html"), encoding = 'UTF-8', knit_root_dir = "C:/Users/cf199/Box/O\'Meara-Taylor Postdoc/mozzie_epitope_analysis")

